Missing The Point

### 2020-09-24 Manuscript.Rmd
Sim results with 25/50/75% incomplete instead of 5/50/95

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results_test.Rdata")

@@

- In this paper we explore diagnostic methods for MICE, and show which parameter has the best performance --> most informative about convergence

@@

- What does non-convergence look like? What are the consequences?

@@

```{r echo=FALSE}
results %>%
  ggplot() +
  #geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>% #filter(it>6) %>% 
  ggplot() +
  geom_hline(yintercept = 0.95, size = 2, color = "grey") +
  geom_point(aes(x=it, y=cov, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=cov, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=CIW, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=CIW, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>% 
  # filter(it>6) %>% 
  ggplot() +
  geom_point(aes(x=it, y=rsq, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=rsq, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

Magnitude of the bias in R^2 perfectly follows the missingness mechanisms: least bias for MCAR, most for MNAR. Worst effect of non-convergence for p=0.95, MNAR, but stable from it=5.

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.mu.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.mu.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.mu.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.mu.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.sigma.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.sigma.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.sigma.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.sigma.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.qhat, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.qhat, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.qhat, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.qhat, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.lambda, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.lambda, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.lambda, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.lambda, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

## Check if heuristic for AC works
```{r}
# load("~/MissingThePoint/Data/diagnostics.Rdata")
# load("~/MissingThePoint/Data/raw_outcomes.Rdata")
sim_nr <- 3
outcomes[[sim_nr]] %>% filter(mech == "MCAR", p == 0.95) %>% ggplot(aes(x=it, y = est)) + geom_line()
convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.qhat)) + geom_line()
convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.lambda)) + geom_line()
```

@@

```{r}
load("~/MissingThePoint/Data/example.Rdata")

# plot example
plotfun <- function(v){
ggplot(example, aes(x = it, y = .data[[v]])) +
  geom_line() +
  theme_classic()
}

@@

load("~/MissingThePoint/Data/example_mids.Rdata")
plot(mids)
```

>>>>

```{r setup, include=FALSE}
# environment
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mice)
load("Data/results.Rdata")

# sim results plotting function
generic_plot <- function(v, name, ...){
  results %>%
    mutate(
      p = factor(p, levels = c(0.05, 0.5, 0.95), labels = c("5%", "50%", "95%")),
      mech = factor(mech, levels = c("MCAR", "MAR", "MNAR"))
      ) %>% 
  ggplot(aes(
    x=.data[["it"]], 
    y=.data[[v]], 
    color = .data[["p"]], 
    shape = .data[["mech"]], 
    linetype = .data[["mech"]]
    )) +
  #geom_point(na.rm = TRUE) +
  geom_line(na.rm = TRUE) +
  labs(
    x = "Number of iterations",
    y = name,
    color = "Incomplete \n cases", 
    shape = "Missingness \n mechanism", 
    linetype = "Missingness \n mechanism") +
  theme_classic() + 
  scale_color_manual(values = c(
    #"#009E73", #green
    "#56B4E9", #blue
    #"#E69F00", #orange
    "#F0E442", #yellow
    "#D55E00"  #red
  ))
  # scale_color_manual(values = c(
  #   # '#228833', #green
  #   # '#66CCEE', #blue
  #   '#CCBB44', #yellow
  #   '#EE6677',  #red~ish
  #   '#AA3377'  #maroon
  #   ))
}
```

@@

- In this paper we explore diagnostic methods for MICE, and show which method (parameter + diagnostic + threshold) is the most informative about convergence

@@

- What does non-convergence look like? What are the consequences? Refer to van Buuren (2018) instead of reproducing it.

@@

```{r echo=FALSE}
generic_plot(v="est", name = "Regression estimate") + 
  list(geom_hline(yintercept = 1, color = "grey"))

@@

```{r echo=FALSE}
generic_plot(v="cov", name = "Coverage rate") + 
  list(geom_hline(yintercept = 0.95, color = "grey"))

@@

```{r echo=FALSE}
generic_plot(v="CIW", name = "CI width")

@@

```{r echo=FALSE}
generic_plot(v="rsq", name = "Coefficient of determination (r^2)") +
  list(geom_hline(yintercept = 0.5, color = "grey"))

@@

Magnitude of the bias in r^2 perfectly follows the missingness mechanisms: least bias for MCAR, most for MNAR. Worst effect of non-convergence for p=0.95, MNAR, but stable from it=5.

```{r echo=FALSE}
generic_plot(v="ac.max.mu.Y", name = "AC chain means")

@@

This plot above and the next three plots show autocorrelations with different thetas

```{r echo=FALSE}
generic_plot(v="ac.max.sigma.Y", name = "AC chain variances")

@@

```{r echo=FALSE}
generic_plot(v="ac.max.qhat", name = "AC scientific estimate")

@@

```{r echo=FALSE}
generic_plot(v="ac.max.lambda", name = "AC novel theta")

```{r echo=FALSE}
generic_plot(v="r.hat.max.mu.Y", name = "R hat chain means")

This plot above and the next three plots show r hat values with different thetas

```{r echo=FALSE}
generic_plot(v="r.hat.max.sigma.Y", name = "R hat chain variances")

```{r echo=FALSE}
generic_plot(v="r.hat.max.qhat", name = "R hat scientific estimate")

```{r echo=FALSE}
generic_plot(v="r.hat.max.lambda", name = "R hat novel theta")

@@

<!-- ## Check if heuristic for AC works -->
<!-- ```{r} -->
<!-- load("Data/diagnostics.Rdata") -->
<!-- load("Data/raw_outcomes.Rdata") -->
<!-- sim_nr <- 3 -->
<!-- outcomes[[sim_nr]] %>% filter(mech == "MCAR", p == 0.95) %>% ggplot(aes(x=it, y = est)) + geom_line() -->
<!-- convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.qhat)) + geom_line() -->
<!-- convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.lambda)) + geom_line() -->
<!-- ``` -->

@@

```{r}
# load data
load("Data/example.Rdata")
load("Data/example_mids.Rdata")

# plot each var of example data
plotfun <- function(v, ...){
ggplot(example, aes(x = .data[["it"]], y = .data[[v]])) +
  geom_line() +
  theme_classic()
}

@@

plot(mids)
```
